Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-09-02 paper.tex
minor fixes

Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40nT$.  The second is an increase in $\rho_{eq}$ above 40~$amu/cm^3$.

Our first analysis uses data only from the time interval 1989-1991.  In this interval, there were (?) $D_{st}$ events and (?) $\rho_{eq}$ events.  For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.  To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours. (Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median dividied by the square root of the number of values used.

In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48~nT$.  Consistent with \cite{Takahashi2010}, $D_{st}$ events corrspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is on the order of $~2 amu/cm^3$ instead of $~10 amu/cm^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non-fill $\rho_{eq}$ value existed.

>>>>

Two types of events are considered. The first is a drop in $D_{st}$ below the threshold of $-40$~nT.  The second is an increase in $\rho_{eq}$ above 40~amu/cm$^3$.

Our first analysis uses data only from the time interval 1989-1991. For both types of events, the hour of the threshold crossing defines the zero epoch time, and for each event $8\cdot24$ hours were kept after each event and $4\cdot24$ hours before each event.  To compute the epoch averages on a daily time scale, the median value of all measurements for all events centered on a window of $\pm 12$ hours was computed, and these windows were shifted in increments of $24$~hours. (Similar results are obtained if we first reduce each event time series to have a 1-day cadence by computing medians in 1-day bins and then compute the medians accross events.)  Error bars for each parameter were computed using (2x ?) the standard deviation of the number of values used in computing the median divided by the square root of the number of values used.

In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.
